Specifying and Verifying the Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
Capitalise contributions

In this paper, we make the following contributions:
%
\begin{itemize}
\item we introduce our specification language for stencils
  that captures many common forms of data access pattern
  (\S~\ref{sec:lang});

\item we detail checking and inference algorithms for our
  specifications (\S~\ref{sec:analysis}), derived from a
  denotational model for the specificaiton language
  (\S~\ref{sec:semantics});

@@

\item we report on a quantitative study of stencil computations on a
  corpus of numerical Fortran programs (ranging from small to large)
  (\S~\ref{sec:evaluation}), totalling one million lines of code. Our tool
  identifies and infers specifications for 35,000 stencil computations in the
  corpus. Approximately 10\% of the stencils we found are non-trivial,
  corresponding to code which is a possible source of errors. This validates
  our hypothesis that the majority of stencil computations have a regular
  shape, and validates the design of our language in its capability to capture
  many core patterns.

>>>>

In this paper, we make the following contributions:
%
\begin{itemize}
\item We introduce our specification language for stencils
  that captures many common forms of data access pattern
  (\S~\ref{sec:lang});

\item We detail checking and inference algorithms for our
  specifications (\S~\ref{sec:analysis}), derived from a
  denotational model for the specificaiton language
  (\S~\ref{sec:semantics});

@@

\item We report on a quantitative study of stencil computations on a
  corpus of numerical Fortran programs (ranging from small to large)
  (\S~\ref{sec:evaluation}), totalling one million lines of code. Our tool
  identifies and infers specifications for 35,000 stencil computations in the
  corpus. Approximately 10\% of the stencils we found are non-trivial,
  corresponding to code which is a possible source of errors. This validates
  our hypothesis that the majority of stencil computations have a regular
  shape, and validates the design of our language in its capability to capture
  many core patterns.
